\chapter{Set ablaze}

\lettrine{T}{he} two of them locked into a predicament. Zyph was caged within Tree between his two arms. His view of the ceiling was eclipsed by Tree's body. Muzzles just a few inches apart. Sharing the same air they exhaled. Tree attempted to hold in his shock, but his panting had betrayed him. Tree's chest moved periodically like the deck of a ship in a turning seas of emotion and anxiety. Trying to steady his breath, trying his beset not to crush his guest under his own weight.

Zyph's hands were buried in Tree's chest fluff, feeling Tree's warmth on his bare beans. Despite it was done out of necessity, Zyph could not help to feel some shred of embarrassment. This feeling raised within him, slowly spilling over onto his cheeks. Zyph's face slowly glowed like the filament of an incandescent bulb. His warming body slowly drove off the condensation on his collar from Tree's breath.

Time seemed to stood still, but Tree's whiskers moving along his breathe, like a clock's second hand ticking, signaling the passage of time. After what felt like an eternity, Tree decided to say something. Being so just inches away from Zyph, Tree asked under his breath, "Are you okay?"

Tree's deep voice was even deeper. Zyph could feel the words with his hands from Tree's chest vibrations. A warm, cosy feeling stirred within Zyph as if he was accepting his fate in this new enclosure. Perhaps it was Stockholm syndrome or it was flight or fight response, Zyph could not help but developed something special to his captor.

"I am fine," Zyph answered, "\emph{uwu}."

Tree retracted slightly from the unexpected answer. Trekking a few inches backwards with his arms, raising himself away from Zyph. Tree did not expect this response from his captive friend. Zyph's words slowly melts into Tree's head as Tree played out all the possible reactions to that answer in his mind. An invitation or a careless slip up. Tree could not decipher it in the heat of the moment.  His eyes narrowed and his whiskers tensed up vibrating like a tuning fork, struck by the shock he received from the ambiguous reply. Spreading like a fire, Tree began to blush. His neck fluff puffed up a little, shortening his neck like an illusion.

"I'm glad you are fine", Tree answered while standing up and offered a helping hand to Zphy to get him off the floor.

Zyph's arms were still hovering aimlessly in the air, regained their directly and accepted the offer. A strange sensation, passing though their hands, surged through them. Being carried along by the momentum, Zyph stood up but fell right into Tree's embrace.

Tree placed his arms around Zphy, his hands exploring Zyph's shoulder, along the chains around his arms. Zyphy's arm around Tree's waist, resting right above his belt pouches. Zphy was buried in Tree's furry chest, listening to his racing heart slowing down to enjoy this special moment a bit longer. True to his name, Tree gave off a refreshing smell of pine needles. Tree tilted his head down and looked into Zyph's eye, his pupils widen pushing the greenness away from his iris.

Zyph looked back at Tree and tipped toe to increase his height to better compliment Tree's shape. Leaning his head and rubbing it against Tree's body slowly, moulding Tree's chest fluff to fit his contour. His tail swept slowly, savouring the moment. The two hugged so closely that you could not tell where Tree ended or where Zyph began. Two souls connected, huddled together in this cold winter night.