% \lettrine{}{} command typesets a drop cap in the document

% second brace set formats text placed inside as small caps
% (same thing as doing \lettrine{L}\textsc{orem ipsum ...}

\chapter{The tech support}

\lettrine{S}{now} fell gently from the sky, dusting the floor with a thin layer of powdered whiteness. It was getting dark slowly, painting an orange shade to the dull grey sky. A cute bean is pacing back and forth by the door. Frustrated, Tree muttered, "What's taking them so long. When will they arrive?"

Tree's trackers were broken, enduring one of the worst scenarios one who trapped indoors on a holiday could. Impatient, tree lowered his stature. Dropping his bottom to the ground, knees bent, arms \mbox{supporting} from behind his back. Fully laid on the floor, Tree threw himself a tantrum. Like a small animal, Tree squeaked and whined, \mbox{flailing} his limps in the air. Like a small child trying to get some attention from his parents, Tree protested to the universe against his misfortune.

However the universe is impartial, they do not take sides and do not care if one fluff is complaining about his circumstances. Little did he know he is about to cross paths with another amazing gem in his life.
\\ \\
\emph{Knock Knock}
\\ \\
Tree paused. Still on his back on the floor, he turned his head \mbox{towards} the door. "I am here to provide tech support for...", said the muffled voice behind the door, "...Treetender." Tree got up to his paws, patted down his fur as an attempt to dust off any evidence of the performance he just gave to an empty audience.

"I'm in." replied Tree as he opened the door. Their eyes did not meet.

"I'm send here to provide tech support for Treetender. I heard you are experiencing tracking issue?" the figure announced, coming from below Tree's sight line. Tree looked down and now their eyes met. Yellow eyes glistened in the dusk. Their grey fur was sprinkled with fresh snow like icing sugar on a pastry. Tufts of white fur forming a fridge running between their pointy ears.

Tree answered, "Yes. Come in."

The grey wolf entered. His chains around his arms rattled like bells ringing, proclaiming their master's entrance. They were attached to a metal collar, loosely fitted around his neck. "You can call me Zyph," said the wolf,"and how can I help you today?" His voice was charming, like a pleasant kind of low pitch hum.

"Call me Tree. I'm experiencing some tracking issue and I can't seem to figure out what's wrong." said Tree, pulling himself out of the transfixing voice of the guest.

Like being dragged by an imaginary leash by the host, Zyph was led into Tree's room. Zyph was quick to work, examining the setup. Zyph scanned the room and paused for a moment. "I think I found the \mbox{problem}," explained Zyph as he gestured towards the space under the sofa, "I think there is something wrong with the cabling under the sofa."

Zyph pulled out something from his trousers, a pen light from his pocket. Switching it on and holding it between his muzzle with another tool in his hand. Zyph looked at Tree as if he was doing a blep with a metallic tongue glowing in the tip. Zyph muttered, "A'll jus' tak a' lor a' et."

Tree could not help but let out a little chuckle. Eager to get to the problem, with another tool in his hand, Zyph in a pouncing motion landed his tummy on the floor and pushed himself under the sofa.
