\chapter{Heating up}

\lettrine{T}{ree} and half a torso of Zyph in the room were engulfed by an awkward silent. In an attempt to break up the still air, Tree asked, "um... So what is you favourite food?"

"My favourite food is broccoli," Zyph answered, "I can go on for hours about why I like it but let's leave that for another time."

Feeling deterred, Tree decided to to have another go at igniting a conversation to drive away the cold silence in the room. Tree asked, "Do you have any hobbies? What do you do in your free time?"

"I sing and play the piano and ukulele" Zyphy answered. Despite not seeing Zyph's face, Tree knew he had done it. As evident by Zyphy's tail wagging proudly in the air, like flames of a freshly ignited campfire, dancing along the rhythmic fanning of the fire starter.

Satisfied by his effort, Tree pushed on,"So what songs do you sing?"

"I sing a lot of sad songs and I like singing in piano ballad style." Zyph answered, hardly containing his enthusiasm,"I even did a piano cover for the song x3 Nuzzles."

They both shared a laughter. The awkwardness had been driven away by the roaring flame they just started. They continued sharing their interests and their stories, fueling the fire. Yet unbeknown to both of them, the fire was burning far hotter than either of them could imagine.

Zyph pushed himself out of the crevice and adjusted himself. "I found the problem," Zyph explained,"the cables have knotted up and was stuck. It is a bit deep but I think I can get to it."

Before Tree could express his gratitude, the nimble wolf flipped over with his back against the floor and gave Tree a smug grin to reassure his confidence. Then pushed himself back into his work space with his strengthen thighs in a two stoke motion. Thrusting himself deeper in the unexplored area of Tree's furniture.

"I think I got it." said Zyph from under the sofa. Zyph attempted to wiggle his legs but they would not budge.

"I think my thighs have gotten thicker from my recent workout. I think I am stuck." said Zyph, with a mixture of embarrassment and a hint of playfulness.

Trying to offer his help, Tree got on all fours. Tree said, "I'm going to pull you out, don't worry." Tree positioned himself between Zyph's legs and wrapped his hands around Zyph's plump thighs. Squeezing them against his knees to get a grip on the smol wolf wedged in the gap. Zyph's thighs were hot like a  glowing poker extracted from a fireplace. Underestimated the girth of Zyph's thighs, Tree re-adjusted his grip and gave it a light tug.

"I think you really got yourself stuck there," said Tree, still pulling and shuffling himself side to side, "I'll give you one big pull. Let me know if it hurts."

Like pulling a stubborn tap root from the ground, Tree pulled with all his strength but also taking care not to hurt Zyph. Tree comically dislodged Zyph from the grasp of the the furniture. Tree lost his balance and fell forward. Both reacted in their own ways as if they had rehearsed this exact situation in their head from watching all the plot required "accidents" in animes. Tree supported his fall with his arms in a push up position and Zyph held his hand up to dampen the weight of the falling Tree.